\documentclass[12pt,letterpaper]{article}
\usepackage[a4paper]{geometry}

\setcounter{secnumdepth}{0}

\begin{document}

\section{General}

BEGIN MISSION STATEMENT

\subsection{Relationship to the University of Minnesota}
\begin{enumerate}
  \item KSG is a Campus Life Program (CLP) of the University of Minnesota,
        Twin Cities and shall abide by the rules and policies of the University
        of Minnesota pertaining to campus life programs.
  \item KSG is associated with the Computer Science \& Engineering (CS\&E)
        Department. As such we receive funding from the department, they assist
        us with promotion and events, and we retain an EFS number for
        within-campus expenses.
\end{enumerate}

\subsection{Non-Profit Nature}
\begin{enumerate}
  \item KSG shall operate as if it were a non-profit organization. All persons
        of KSG are prohibited from profiting directly from the activities of
        the group.
\end{enumerate}

\subsection{Non-Discrimination Policy}
\begin{enumerate}
  \item KSG shall not discriminate against any person on the basis of gender
        identity; sexual orientation; sex; race and ethnicity; color; age;
        disability; socioeconomic status or background; religious or spiritual
        beliefs or lack thereof; political affiliation; public assistance status;
        veteran status; marital or familial status; national origin; residential
        status; or openness of any of the aforementioned.
\end{enumerate}

\section{Membership}

\subsection{Eligibility}
\begin{enumerate}
  \item Any person or institution subscribing to the purposes of the Association
        and eligible for membership in accordance with this Constitution will
        become a member upon the acceptance of written or verbal application
        for membership.
\end{enumerate}

\subsection{Membership}
\begin{enumerate}
  \item Membership shall be granted to persons who attend a minimum of 2 meetings.
        Any officer shall grant membership on request given eligibility has been met.
\end{enumerate}

\subsection{Resignation}
\begin{enumerate}
  \item A member may at any time file for resignation by submitting a written
        statement to the Secretary or the official KSG UMN email address,
        EMAIL. Resignation shall become effective as of the date it is filed.
\end{enumerate}

\subsection{Admonition, Suspension and Expulsion}
\begin{enumerate}
  \item A member of the Association may be admonished, suspended or expelled
        given lack of integrity or violation of rules after agreement by
        the executive committee. Any formerly expelled member of the Association
        may become a member again only after approval of their application by
        a majority vote of a quorum.
\end{enumerate}

\section{Required Officers}

\subsection{Titles}
\begin{enumerate}
  \item The officers of the Association shall be at least a President, a
        Vice-President, and a KSG board that includes a Treasurer, a Secretary
        and any number of additional officers.
  \item The President, Vice-President, Treasurer, Secretary, and additional
        board members shall be collectively referred to as the Executive Committee.
\end{enumerate}

\subsection{The President}
\begin{enumerate}
  \item The President shall act as President of the Executive Committee and KSG
        Officers.
  \item The President must be consulted in the event of officer declaration
        or resignation.
  \item The President holds responsibility to guide KSG and mediate any conflict
        that may arise during operation.
\end{enumerate}

\subsection{The Vice-President}
\begin{enumerate}
  \item In the temporary absence or incapacity of the President, the Vice-President
        shall act as President of the Executive Committee and of the Officers.
        In the absence of both President and Vice President, the Officers shall elect
        a President \textit{pro tempore} from among its membership to act for a
        period to be determined by the Officers.
  \item The Vice-President shall be responsible for overseeing and assisting both the
        Treasurer and Secretary in their duties.
\end{enumerate}

\subsection{The Treasurer}
\begin{enumerate}
  \item The Treasurer, or other assigned officer, shall provide for custody of the
        original of this Constitution and of the amendments thereto.
  \item The Treasurer, or other assigned officer, shall provide for custody of the
        seal of the Association, and when authorized by the Officers or the Executive
        Committee shall affix it to any instrument of the Association requiring a seal.
  \item The Treasurer shall ensure that dues and other sums are collected, that all
        properly approved bills are paid, and that financial statements and budgets
        are prepared. The Treasurer shall render to the Officers or the Executive
        Committee, as required, an accurate account of all transactions and of the
        financial condition of the Association. These are referred to as the required
        reports.
\end{enumerate}

\subsection{The Secretary}
\begin{enumerate}
  \item The Secretary, or other assigned officer, shall ensure that records are kept
        of all proceedings, actions and meetings of the Association, the Officers,
        and the Executive Committee, and that the votes and minutes thereof are
        recorded in a book or books to be kept for that purpose.
  \item The Secretary, or other assigned officer, shall conduct the correspondence of
        the Association and shall give due notice of all meetings of members, of the
        Officers, and of the Executive Committee.
  \item The Secretary, or other assigned officer, shall provide for the maintenance
        of a list of all members of the Association, clearly designating those
        entitled to vote, and such list or a copy thereof shall be made available for
        inspection by the members at all meetings of the Association where votes of
        the members are taken.
\end{enumerate}

\subsection{The Faculty Sponsor}
\begin{enumerate}
  \item The Faculty Sponsor shall be a voting member of KSG and either a member of
        the faculty or full-time staff of the University of Minnesota Twin Cities.
  \item The Faculty Sponsor shall be generally responsible for the activities of the
        group. Specifically, the Sponsor:
  \item Provides continuity from year to year, remaining a constant presence as
        student leadership and personnel change.
  \item Promotes good student-faculty relationships.
  \item Ensures that the policies and standards of the University are upheld in all
        activities of the group.
  \item Exercises financial supervision, if necessary, by promoting prompt payment of
        bills and collection of dues as well as overseeing the settlement of all
        accounts in the event of dissolution of the group.
  \item Represents the group's interests to faculty and administrators.
\end{enumerate}

\subsection{The Board}
\begin{enumerate}
  \item Any additional KSG board member shall be appointed by the Executive Committee from
        the pool of the elected officials.
  \item The board facilitates a flat distribution of power in KSG. The President, Vice-President,
        and board members shall have equal vote in administrative decisions.
  \item The President and Vice-President retain the ability to challenge and overturn any
        decision made by the board that fails to accurately represent the interest of KSG.
  \item In the event of an equally split quorum, the President retains the ability to
        break the tie with KSG's best interest in mind.
\end{enumerate}

\section{Executive Committee}

\subsection{Composition and Authority}
\begin{enumerate}
  \item The Executive Committee shall consist of the President, the Vice-President, the
        Treasurer, the Secretary, and the remaining KSG board members.
  \item The Executive Committee shall be bound by any action taken by the Officers or
        the Association. The Executive Committee shall appoint representatives of the
        Association for specific purposes, and shall in general manage the affairs of
        the Association between Officer meetings except in those matters for which
        Officers action is required by the Constitution. The President shall
        call a meeting of or cause questions to be presented to the Executive
        Committee upon the request of any member of the Committee.
  \item No official business of the Chapter shall be conducted unless a quorum is
        present. A quorum of the Officers shall be defined as a majority of the
        Officers or two Officers and one quarter of Members.
\end{enumerate}

\subsection{Authority to Act Without Meeting}
\begin{enumerate}
  \item Any resolution adopted by majority vote of the Executive Committee after
        due notice to each of its members shall be deemed and considered the act
        of the Executive Committee as though adopted at an actual meeting of the
        Committee whether or not on the occasion of the vote there was an actual
        meeting of the Committee. The notice and the voting of the members
        of the Committee may be by mail, telephone, telegraph, electronic
        communication, or personally, or by any combination of these, and notice by
        mail or telegram shall be deemed given when sent to the Committee member's
        last mailing address. A record of the notice and of the voting and of the
        manner in which the action was taken shall be noted in the minutes of the
        Committee.
\end{enumerate}

\subsection{Place of Meeting}
\begin{enumerate}
  \item Meetings of the Executive Committee shall be at the principal office of the
        Association, or at the place of and in connection with a meeting of the
        Association, or at such places as the Executive Committee may determine.
\end{enumerate}

\section{Officers}

\subsection{Membership}
\begin{enumerate}
  \item All Required Officers are required to be Members of the Association.
  \item Officers of the group will be currently enrolled University of Minnesota -
        Twin Cities campus student who are registered for at least six credits.
        Graduate and Professional students can be exempted from the credit
        requirement with documentation from their program signifying the student is
        actively pursuing a degree. Officers must also be in good standing with the
        University and free from any sanctions as defined in the Board of Regents
        Policy - Student Conduct Code, administered by the Office for Community
        Standards.
\end{enumerate}

\subsection{New Officer Positions}
\begin{enumerate}
  \item New officer positions may be established by a majority vote of quorum.
  \item An officer may be Titled or Untitled.
  \item Untitled Officers may be referred to as General Officers.
\end{enumerate}

\subsection{Authority and Duties}
\begin{enumerate}
  \item The Officers shall formulate the policies of KSG, and generally supervise
        their execution. Each Officer shall represent the members and the best
        interests of the Association.
  \item Each officer of the Association shall be bound by any action taken by the
        Officers or the Association and shall have such additional authority and
        duties as may be conferred this Constitution and resolution of the Officers.
\end{enumerate}

\subsection{Meetings}
\begin{enumerate}
  \item The Officers shall meet weekly. A quorum of the Officers shall consist of a
        majority of the Titled Officers, or two Officers and one quarter of Members.
  \item KSG shall hold meetings only in places that are open and accessible
        to all members of the Association.
  \item An Officer unable to be present at a meeting may appoint a Member of the
        Association as the Officer's proxy. The proxy may take part in discussion and
        may vote in the place of the Officer. While so acting as a proxy for the
        Officer, the proxy shall be deemed for all purposes to have the powers of
        that Officer for whom they stand in, but only in the absence of the replaced
        Officer. Proxy appointment shall not be longer than one meeting in duration.
  \item Except where by law or by this Constitution a meeting of the members of the
        Officers or their proxies requires their physical presence at the same time
        and place, the Officers may transact business by mail, electronic
        communications, in the physical presence of each other, or by any combination
        of these means. Any resolution adopted in such manner by a majority vote of a
        quorum of the members of the Officers (or by such larger vote as may be
        required by law or by this Constitution), after due notice is
        given to its members shall be deemed and considered the act of the Officers
        as though adopted at a meeting of the Officers. Notice by mail or electronic
        communications shall be deemed given when sent to the Officers member's last
        address. A record of the notice and of the voting and of the manner in which
        the action was taken shall be noted in the meeting minutes.
  \item Actual meetings of the Officers are required to be held at least once in
        Spring Semester and once in Fall Semester.
\end{enumerate}

\subsection{Annual Budget}
\begin{enumerate}
  \item Each year, the Officers shall adopt an annual budget authored at least in
        part by the Treasurer. This budget shall guide the fiscal affairs of the
        Association for the following fiscal year.
\end{enumerate}

\subsection{Questions}
\begin{enumerate}
  \item The Officers shall give members of the Association reasonable opportunities
        to express their views on presented questions to the Association upon request
        of the inquisitor. Upon petition of one percent of the Members of the
        Association or by decision of a majority of the Officers, a question to the
        Association shall be submitted without undue delay to a ballot of the
        Association as provided in the Constitution. The majority vote where quorum is
        present shall be binding upon the Officers, except where a larger vote is
        required by law and except in the case of an amendment to this Constitution
        or the Certificate of Incorporation.
\end{enumerate}

\subsection{KSG Code of Professional Ethics}
\begin{enumerate}
  \item The Officers shall adopt, maintain, enforce, and conspicuously publish and
        display to all members and the public a code of professional ethics, which
        shall be binding on all members of the Association.
\end{enumerate}

\section{Elections}
\begin{enumerate}
  \item The President, Vice-President, Treasurer and as many Officers as are required
        to fill Officer vacancies shall be elected as of the end of Spring Semester every
        year by the Members of the Association.
  \item Officers shall be elected by a plurality of the votes cast at the annual election
        meeting.
  \item A majority of votes of members composing quorum shall be required to carry a motion.
  \item Currently registered students at the University of Minnesota - Twin Cities campus
        shall comprise no less than 2/3 of the group's total voting membership. 
  \item No person may hold two Officer positions simultaneously.
  \item Appointment or nomination of an individual to an officer position within KSG
        UMN shall be limited to two full consecutive terms in the same position.
\end{enumerate}

\section{Tenure}

\subsection{Officers}
\begin{enumerate}
  \item All officers shall be elected for one year terms.
  \item If any vacancy arises in an Officer position, the Executive Committee shall
        fill it by appointment until the next regular election.
\end{enumerate}

\subsection{Recall}
\begin{enumerate}
  \item Any elected Officer may be recalled by vote of the Members following an
        impeachment. Impeachment must be by a vote of one fourth of members present
        where quorum exists. Upon impeachment, the Officers shall promptly direct a
        special ballot by all Members. A majority vote of the votes given quorum will
        suffice for immediate removal of an Officer from their Officer position.
\end{enumerate}

\section{Nominations}
\begin{enumerate}
  \item Members shall be notified of nominations for Officers as provided in the
        Constitution. Prior to distribution of the ballot, nominations by petition of at
        least one percent of the Members of the constituency shall be received and
        entered on the ballot in the manner described in the Constitution.
\end{enumerate}

\section{Association Meetings by Ballot}
\begin{enumerate}
  \item With respect to any question or vote required by law to be submitted to or
        taken by the Members of the Association at a meeting of the Members, the
        timely emailing of the ballot or other notice to each Member at the last
        email address as given to the Treasurer, or other appointed officer, shall be
        deemed and considered notice of a meeting of the Association; the return of
        the ballot shall be deemed a counted vote. Each Member of the Association,
        however, shall have the privilege of attending in person at the time and
        place stated in the ballot or other notice for the opening and counting of
        the ballots, and the Member may cast a vote personally instead of by online
        ballot.
\end{enumerate}

\section{Amendments}

\subsection{Constitution}
\begin{enumerate}
  \item This Constitution may be amended by an affirmative majority vote of quorum.
        Proposed amendments to this Constitution shall be submitted to the quorum for
        ballot upon an affirmative vote of two-thirds where quorum exists.
  \item This Constitution may be adopted or amended by a majority vote of quorum. The
        Officers shall have the authority to interpret this Constitution.
\end{enumerate}

\subsection{Notification}
\begin{enumerate}
  \item Any additions or changes in the Constitution shall be reported by the Treasurer,
        or other appointed officer, to the membership by mail, email, or publication in
        one of the Association's publications received by all members.
\end{enumerate}

\section{Dissolution of KSG}
\begin{enumerate}
  \item Dissolution of KSG by consent of the members shall consist of unanimous
        agreement of all its officers together with a majority vote at a meeting.
        This meeting must have been publicized at least two weeks in in advance
        to all members of the KSG as for the purpose of taking this vote of
        dissolution.
  \item Should KSG be dissolved, its assets and liabilities shall be
        transferred to the College of Science and Engineering.
\end{enumerate}

\end{document}
